%mainfile: ../../master.tex
\section{User Scenarios}\label{sub:userscenarios}

Below are possible narratives of branches derived from the use cases, as described in \cref{sub:usecases}. It is not possible to describe every possible uses of the system, as there are infinitely many, even though the user scenarios below can be used as unit tests for the system; given some behaviour does the system act as describe in the scenarios?

\textit{A user is reading a book, the light intensity of the sun is low now due the time of the day, and the user is having trouble reading. The system has learned that at this light intensity when the user is situated at the couch with TV not running, the user now wants the light to be on.}

\textit{A user is home alone in his/her living room. The user leaves the room to go to the toilet but does not turn off the light in the living room, while on the toilet the user closes the door and does not observe the light in the living room being turned off by the system to conserve/save energy.}

\textit{A user just left home for a vacation. The user forgets to turn off some lights, the system recognises this and switches the lights off. The user has not been home for 24 hours, the system now initiates in doing short cycles of simulating normal behaviour of the user in some rooms to seed the impression of someone being home, to pro actively prevent attracting interest from any observing burglars.} \kanote{Skal den det?}

\textit{In a financial report an organisation recognises a substantial amount of funds is used on lighting the facility. The system generates a report on the lights around the facility, effective lighting hours. Which the supervisors can conclude on to argue were to invest on more energy efficient lighting. Further the system reports on broken or not functioning lighting.} \kanote{Skal den det?}

%Just for fun ? Many users is situated in the living room and the volume(db) of the stereo is really high, so users is shouting to hear each other and this occurs over prolonged duration, the system intelligently lowers the volume without the user noticing. And at 1am/pm(night) the user normally goes to sleep but not today, but because of neighbours the system lowers the volume further.
