\section{XBee}\label{sec:xbee}
As discussed earlier, communication in the system will be done through XBee modules, using the ZigBee protocol\kanote{this is the first time we mention xbee.. awkwaaaard}. In this section, the specific implementation for using the XBee devices will be discussed, along with some calculations of the worst case execution time of this part of the system.

The following calculations define the theoretical timings for sending packets using XBee modules.

\begin{equation*}
\text{BACKOFF} = \sum\limits_{R=0}^{n=4}(2^{R} - 1) 0.320 + 0.128_{CCA} ms = 8.96 ms
\end{equation*}
Where $R$ denotes the number of retries, $n$ denotes the maximal number of retries, $CCA = \text{Clear Channel Assessment}$.

For this project we use 64 bit unicast, due to the considerations made in \cref{sec:xbee}.
Transmission time of a 64 bit packet is given by $T_{\text{air}}$
\begin{equation*}
T_{\text{air}}(B) = 0.8_{\text{header}} + 0.032B_{\text{payload}} ms
\end{equation*}
Where $B$ is the number of bytes in the packet, $T_{\text{air}}(72) = 3.104 ms$ is the maximum transmission time as 72 bytes is the maximum payload for the ZigBee protocol\cref{xbee_latency}

The worst case time of a packet being transmitted and being received before just getting dropped is given by $\text{WORST}$ assuming the ACK arrived 0.1ms before ACK wait timer ran out.
\begin{equation*}
\text{WORST} = (\text{BACKOFF} + T_{\text{air}}(72) + 0.864_{\text{wait for ACK}})*4_{\text{maximum number of retries}} - 0.1 ms = 51.612 ms
\end{equation*}
Note that the worst case increases, the more retries are added, to increase reliability of a packet arriving.

\subsection{Sending Modes}
The XBee module has two different control interfaces; transparent- and API mode.
\subsubsection{Transparent Mode}
In transparent mode, whatever the XBee module receives on its serial input pins, it immediately sends over the network to the address specified in the firmware settings. Unless the client/host program handles it, there is no guarantee that a package is received. \cref{arduino_at_mode}
In this mode, a lot of messages can be sent quickly, but with little control.
%https://docs.digi.com/display/WirelessConnectivityKit/Command+mode
\subsubsection{API Mode}
In API mode, the XBee module buffers the data, it receives on its serial pins, to a limit of 64 bytes, until a specific command is received. If it receives a send command, it packages the data in its buffer in the ZigBee protocol\footnote{The ZigBee protocol is IEEE 802.15.4 based}, which includes the module's address and network information, and makes the receiving module send back a received acknowledgement (except if broadcasting). In addition the protocol implements either a beacon frame or a exponential back off algorithm. A beacon frame asks for permission to use the network, then the coordinator of the network makes sure no other modules transmits while the asking module uses it. An exponential back off algorithm waits a random amount of time before re-sending the collided package, if the collision happens again it waits an incremental amount of random time. The XBee documentation does not specify which of these methods is implemented however the beacon frame is not definable in XBee, so it is assumed that the XBee module uses exponential back off. This process creates overhead, resulting in the time to send (including receiving the acknowledgement) taking up to be around $50$ ms, as calculated above. However, it is possible to ignore the acknowledgement, this means the time to send is lowered significantly.

\subsection{Implementation}
While there should be no single sensor state, so significant, that the system would take a considerable precision hit, in the case it gets lost. The actions which the server sends needs to always reach its client, for this reason this system uses the API mode, so that we get an acknowledgement.

\subsubsection{Arduino Implementation}
Using the XBee library\cref{xbee_arduino_library} for Arduino, simple calls to the Arduino is facilitated through the C++ objects given in the library. Sending is handled by passing a send command  to the module, the system then waits a maximum of 250 ms for a acknowledgement. Packets are send using 64-bit addressing, as this is what is supported for series 2 XBee modules.
Receiving data is done, using predefined call back methods from the library. A single method call ensures that every kind of package is processed, and the method for handling the relevant packages can be overwritten. The relevant package for the Arduino is the zbReceive, i.e. the package that contains user defined data. On the Arduino, the only possible data, this can contain, is an action, so the overwritten method decodes and performs the appropriate action.
%https://github.com/andrewrapp/xbee-arduino
