\section{Test and Verification}
In this section a description of the testing performed on the system to verify that it, to a satisfying degree, solves the problem solution. Along with this description a number of alternatives wil also be discussed in relation to why they weren't chosen.

\subsection{Testing}
To test the system, we set up a simple test system in a controlled envoirment. Consisting of just one sensor an emulatable action and the server. Then for *\ranote{insert how many hours we actually performed it} we performed a very deliperate pattern. A pattern here consisting of an action and a change in the sensor state. Then we stopped performing the action, and if the system took over and performed the action when the sensor state changed it would be considered succesful. This is the simplest use case for the system, but shows that our machine intelligence can regocnize a pattern which is also the smallest requirement for the system to be deemed working. Once the machine intelligence has been tested the real-time critical part of the system (from the sensor station through the reasoner back to the sensor station) were tested \ranote{Real time test lingo? Ignore? Specifik real time test method?}...*
\\\\
Once it has been verified the system can learn a pattern and can reason and subsequently perform the appropriate action within a *time frame*\ranote{see last note} the second key component of the system is the ability to adapt to a change in pattern. So following the first test, ie. the system has a learned pattern, a different overlapping pattern were performed for an hour. Then we checked if the system had adapted, if not the pattern were performed for another hour this were repeated until the system adapted. While it is important noting how quickly the system adaptes to change once it has been confirmed the system does adapt the speed with which it does can be changed.
\subsubsection{Results and Specific Setup}
%gogo write stuff

\subsection{Alternative tests}
The first alternative which were considered is a real world use case. In this test a system would be setup in a(or more) users home for a given set of time. Once the test had finished the log data from the system along with user testimony would determine the performance of the system. This test is very time consuming, because the system would need to be live for an extended periode of time to learn user patterns on a daily, weekly, or longer scale. The log data can also be difficult and time consuming to analyse because the very large amount of data processed by the system and the difficult to visualy represent machine learning model used.
%more examples or rephrase intro?