\section{Hardware}
As decided in \cref{sec:architecture}, the system should consist of 2 subsystems: a sensor/actuator subsystem and a artificial intelligence subsystem. \sinote{Dette er under antagelse af at vi har valgt arkitekturen der sender regler til sensor subsystem}. This section will summarise the hardware requirements for the 2 subsystems, and at the end choose which hardware is suitable choices.

\subsection{Sensor/actuator Subsystem}
The sensor/actuator subsystem consists of sensors, actuators and computational devices driving the sensors and actuators. \Cref{sec:requirements} lists some properties that the system should be able to monitor. \Cref{sec:architecture} specifies requirements for the computational devices driving the sensors and actuators. The following section discusses different hardware components that could fulfil the requirements. \sinote{Vær opmærksom på afsnit herunder svarer til sensorkrav fra analysen + tjek om overskrifterne matcher}

\subsubsection{Time}
Time can be measured using a real-time-clock component. This component is driven by its own battery, so it can run regardless of whether the hardware platform it is connected to, has power.

An alternative method of keeping track of time is by using an internal clock on the hardware platform that controls the sensors and actuators. This clock will only work when the platform has power. This means that every time the hardware platform is started, the clock is reset, so the correct time has to be determined.

In the context of this system, it is important that every component of the system has the same notion of time. The time has to be synchronised between all subsystems. This is true even for the real-time-clock components, as even a slight drift in time would result in different notions of time across the whole system. One can therefore argue that the persistence property of a real-time-clock is not needed. An internal clock in the hardware platform is adequate, as long as it is synchronised sufficiently often with other devices in the system.

\subsubsection{Light Intensity}
To measure light intensity, photoresistors are often chosen because of their small size and low cost. These properties fit the requirements of the system very well. In this project, the \enquote{VT90N2} photoresistor is chosen, because of its availability. Further information and experiments can be found in \cref{sub:photoresistor}.

\subsubsection{Location and Spatial Awareness}\sinote{Der skal måske specificeres at det er awareness af brugeren?}
The location of the user can be determined by a motion sensor. One example of a accessible motion sensor is a passive infrared sensor (PIR). These type of sensors are small in size, and low in cost. The specific PIR sensor used in this project is \enquote{SEN32357P}, because of its availability. Additional information and experiments on this sensor can be found in \cref{sub:pir}.

Spatial awareness can be achieved with a distance sensor. In this project, ultrasound distance sensors will be used. The sensor is small in size, and does not cost much. The specific component used has the part number \enquote{\sinote{hvad er part number?}}. It was chosen because of its high availability. See \cref{ultrasound}\sinote{indsæt rigtig reference til ultralydssensor afsnit når det er skrevet} for more information and experiments.

\subsubsection{Awareness of active devices}
To determine whether a given appliance is turned on, one can measure the number of watts it draws. A voltmeter can do this.

\subsubsection{Control of lightning and appliances}
To control lightning and appliances, one has to have a way to conditionally allow current to flow. This can be achieved with a relay. In this project, the relay used has the part number \enquote{\sinote{skriv rigtigt part number når vi ved det}}. More information can be seen in \cref{x}\sinote{afsnit i implementation omkring relays}.

\subsubsection{Input/output pins}
It is obvious that the computational device controlling the sensors and actuators has to have sufficient number of pins for connecting said sensors and actuators.

\subsubsection{Memory capacity}
As specified in \cref{sec:architecture}, rules are to be stored on the computational devices controlling the sensors and actuators. As specified in \sinote{referer afsnit hvor vi snakker om regler}, a rule has the size of x \sinote{Indsæt rigtigt tal når det er klart} bytes. The hardware platform should be able to store x \sinote{indsæt rigtigt tal} rules at any given time.

\subsubsection{Computational Performance}
The chosen architecture for the system, as described in \cref{sec:architecture}, does not have a strict requirement on the computational performance of the hardware platform controlling the sensors and actuators.

\subsubsection{Scheduling options}
In \cref{sec:architecture}, the chosen architecture describes that the sensor and actuator controllers have two functions: control its sensors and communicate monitored sensor data to other devices. To precisely control when actions happen on the platform, it should be possible to manually schedule tasks to run.

\subsubsection{Price}
The conclusion of the analysis, as described in \cref{sec:requirements}, lists price as an important criteria.

\subsubsection{Energy efficiency}
\Cref{sec:requirements} lists energy efficiency as an important property the system should have. This means that the hardware platform controlling the sensors and actuators has to consume a small amount of energy in use.

\subsubsection{Choice of hardware platform}
Arduino Uno boards are chosen for controlling the sensors and actuators. The Arduino boards were already available for our use, so no hardware was needed to be purchased. However, the Arduino Unos also fulfil all the above requirements for the hardware platform.

\subsection{Artificial Intelligence Subsystem}

\subsubsection{Computational Performance}
As described in \sinote{reference}, there are no deadlines involved in the AI subsystem. This means that there essentially is no requirement for the performance. However for the system to be usable, the subsystem should not take forever to generate rules. The computations the subsystem has to perform are described in \cref{sec:ai}. The hardware platform used in the sensor/actuator subsystem is not powerful enough to perform these computations in reasonable time. Therefore more powerful hardware is needed.

\subsubsection{Input/output pin availability}
The AI subsystem has to have accessible input and output pins in order to attach radio modules to the AI computational device.

\subsubsection{Choice of hardware}
The Raspberry Pi is chosen as the hardware of choice for the AI subsystem because of it was already available to us. The Raspberry Pi is estimated to be powerful enough to compute the required computations in reasonable time. It also fulfils the second requirement about input/output pins.
