%mainfile: ../master.tex
\section{Device Communication Protocols}

All the devices installed in a automated home need some form of communication
method with other devices in order to send/receive data. For example, a light
bulb might need to know when to turn itself on. Another example could be
sending data collected from a temperature sensor to another device.

This section explores some protocols frequently used in the domain of home
automation. Each protocol has some characteristics that is outlined below.

\subsection{X10} \cite{wiki_x10}

\begin{itemize}
\item Designed in 1975
\item Supports both power line and wireless installation
\item Lacks encryption
\item Limited reliability
\end{itemize}


\subsection{Universal Powerline Bus} \cite{wiki_upb}

\begin{itemize}
\item Released in 1999
\item Powerline based
\item Limited bandwidth of 240 bits/s
\end{itemize}


\subsection{Insteon} \cite{wiki_insteon}

\begin{itemize}
\item Supports both power line and wireless installation
\item Proprietary
\item Compatible with X10
\item Uses power line as backup in case of wireless interference
\item Theoretical bandwidth of 2880 bits/s
\end{itemize}


\subsection{Z-wave} \cite{wiki_zwave}

\begin{itemize}
\item Wireless
\item Proprietary
\item Theoretical bandwidth of 100 kilo bits/s
\item Line of sight range is approx. 100 meters
\item Designed for low power consumption
\end{itemize}


\subsection{ZigBee} \cite{wiki_zigbee}

\begin{itemize}
\item Originally designed in 1998, standardised in 2003 and revised in 2006
\item Based on IEEE 802.15.4 open specification
\item Wireless
\item Line of sight range is 10-100 meters
\item Theoretical bandwidth of 250 kilo bits/s
\item Designed for low power consumption
\end{itemize}

\subsection{WiFi} \cite{wiki_wifi}

\begin{itemize}
\item Wireless
\item Designed for high-bandwidth rather than low-power consumption
\item Open standard
\end{itemize}


\subsection{Bluetooth} \cite{wiki_bluetooth}

\begin{itemize}
\item Wireless
\item Designed for short-range, low-power consumption
\item Ranges vary from 1 meter to 10 meters to 100 meters for industrial use
\end{itemize}

\subsection{Ethernet} \cite{wiki_ethernet}

\begin{itemize}
\item Wired connection
\item High bandwidth - 100 gigabit/s
\item Low latency
\end{itemize}

Some observations can be made about the listed protocols. Considering the
use-site of the devices, homes, wireless protocols seem most fitting. Protocols
designed for low power consumption are a must when the devices using the
protocol are battery-based. However they do not allow for high data transfers
and a high range.
