\section{System Definition}

This section formally describes in which context the system is to be used, its
expected functions, the philosophy of the system, the conditions in which the
system is used, the technological aspect of the system, and the objects the
system should recognise and process.

\subsection{FACTOR}

The definition of the system can be decomposed into functionality, application
domain, conditions, technology, objects, and responsibility. This forms the
acronym FACTOR as introduced in \cite{mathiassen2001objektorienteret}.

\subsubsection{Functionality}

The system should be able to learn usage patterns of users, and repeat them autonomously, still taking into consideration the possibility of temporary exceptions to daily routines.

\subsubsection{Application Domain}

The system is meant to be used in homes where one or more users live. Each user may
have different usage patterns and sometimes irregular actions not part of their
daily routine.

\subsubsection{Conditions}

The system aims at reducing user interaction as much as possible.

\subsubsection{Technology}

The system should have small devices with accommodating sensors and actuators scattered strategically placed inside the home.
These devices should be energy efficient in their use. Another computational
device should analyse sensor data collected by the small devices and, based on
the analysis, create behavioural rules for the devices to follow and create an autonomously automated system.

\subsubsection{Objects}

The system should recognise the users' patterns and their interaction with the
rest of the home.

\subsubsection{Responsibility}

The system should be as invisible as possible, only creating behaviours that are always aligned with the users wishes. Meaning that the system should never create a rule that is only sometimes true, thereby annoying the user. This is done to minimise friction between the system and the user. This means that the user should not be frustrated about the actions performed by the system. To achieve this the system should be conservative about its actions as to not perform actions the user would otherwise not have made.

\subsection{Requirements}

The system should ease the lives of its users by performing actions autonomously
on their behalf. These actions should be learned by monitoring users' usage
patterns throughout the day. As the user may perform irregular actions, the
system should be conservative about performing actions. The systems should
therefore only perform actions when it has a understanding of the action
pattern. The system should be as invisible to the user as possible. The system
should be an aid, not an element of frustration. The system should use small
computational devices, that save energy consumption, to monitor the usage
patterns of the users. The data acquired in this way should be sent to another
computational device that analyses it, to further improve the knowledge of the
users' behavioral patterns, thereby improving the quality of actions the system can perform.
